The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
edit fitness P6

Multilayer networks further provide unique challenges and opportunities for understanding the social phenotypes and environments of individuals and their fitness outcomes. Picking the proper temporal scale is important but a challenge because all layers in the multilayer network should be made for the same time period, and the period needs to be long enough for each layer to have enough data for robust networks (Farine, 2017). These considerations may be limiting factors when answering questions that require timeframes that are relevant to different individuals. On the other hand, multilayer network metrics provide an opportunity to help simplify statistical models. Interactions that happen mere meters apart, proximity associations, and long-distance interactions can be encapsulated in one network to gain a single metric to describe the various social scales of an individual’s network position. This multilevel network metric would be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014). This method could be an alternative to using PCA to simplify many social network metrics into one social phenotype (e.g. Foster et al., 2012; Oldham et al., 2019). Future analyses should explore the differences in how well each of these methods describe and predict fitness outcomes of the complex social network positions of individuals.

>>>>

Multilayer networks further provide unique challenges and opportunities for understanding the social phenotypes and environments of individuals and their fitness outcomes. Picking the proper temporal scale is important but a challenge because all layers in the multilayer network should reflect the same time period, and the period should be long enough for each layer to have enough data for robust networks (Farine, 2017). These considerations may be limiting factors when answering questions that require timeframes that are relevant to different individuals. On the other hand, multilayer network metrics provide an opportunity to simplify statistical models. Interactions that happen meters apart, proximity associations, and long-distance interactions can be encapsulated in a single multilayer network and a single metric can be used to describe the various social scales of an individual’s network position. This multilevel network metric could be used to assess the relationship between an individuals social phenotype and fitness. It would also be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014).
